---
title: "ASA Data Challenge Report"
author: "Ran Liao & Zedong Wu"
date: "11/8/2020"
output: html_document
---
```{r setup, include=FALSE}
source("Analysis_2016.R")
source("Analysis_2018.R")
```

## 2016 VS 2018
### What is the voting participation percentage for each race and/or by gender across the nation?
```{r echo=FALSE}
turnout_barplot_interactive_2016


turnout_barplot_interactive_2018
```


```{r echo=FALSE}
turnout_sex_interactive_2016

turnout_sex_interactive_2018
```

### What is the voting participation percentage for each state across the nation?
```{r echo=FALSE}
turnout_state_2016_interactive

turnout_state_2018_interactive
```


### What are the relatively more common reasons for people who are in the least-participated races or most populated races to not vote?
#### Nation Wide
```{r echo=FALSE}
nvote_reason_2016

nvote_reason_2018
```

#### Least-participated Races in 2016
##### American Indian-Asian
```{r echo=FALSE}
nvote_reason_aia_2016
```

##### American Indian/Aleut/Eskimo
```{r echo=FALSE}
nvote_reason_aiae_2016
```

##### Hawaiian/Pacific Islander only
```{r echo=FALSE}
nvote_reason_hpio_2016
```

##### White-Asian-Hawaiian/Pacific Islander
```{r echo=FALSE}
nvote_reason_wahpi_2016
```
#### Least-participated Races in 2018
###### White-Black-Asian
```{r echo=FALSE}
nvote_reason_wba_2018
```

##### White-American Indian-Asian
```{r echo=FALSE}
nvote_reason_waia_2018
```

##### Asian-Hawaiian/Pacific Islander
```{r echo=FALSE}
nvote_reason_ahpi_2018
```

##### American Indian/Aleut/Eskimo
```{r echo=FALSE}
nvote_reason_aiae_2018
```

#### Most-populated Races
##### White
```{r echo=FALSE}
nvote_reason_white_2016

nvote_reason_white_2018
```

##### Asian
```{r echo=FALSE}
nvote_reason_asian_2016

nvote_reason_asian_2018
```

##### Black/Negro
```{r echo=FALSE}
nvote_reason_black_2016

nvote_reason_black_2018
```

#### What are the relatively more common reasons for people to not registered to vote?
```{r echo=FALSE}
nreg_reason_2016

nreg_reason_2018
```

#### Is there any voting methods preferences across state?
```{r echo=FALSE}
vote_method_state_2016

vote_method_state_2018
```
